From Freebase to Wikidata: The Great Migration

### 2015-10-13 paper.tex
Removes an outdated sentence
Wikidata now supports quantities with units
Beggining of 4.1

\todo{Denny: write me}

@@

\todo{Sebastian: write me}

@@

From the Freebase dump we have been able to create more than 17M~Wikidata claims
(\emph{i.e.}, statement without references) including 1.5M~IDs.
For that we have used 31M~facts.
When we add some references we get 19.6M~statements, and, after removing 1M~of duplicates
and the ones already in Wikidata, we obtain 14M~new statements.
So, if all these statements were added to Wikidata,
it would lead to a~21\% increase of Wikidata statements number.
But why are these numbers so low compared to the size of Freebase?
We believe that the main reason is that we have only mapped to Wikidata 4.56M~items, (\emph{i.e.},
only 9.5\% of Freebase topics), that are the subject of only 64M~facts.
So, we could not hope to map more than 64M~statements
assuming that we could map all reverse properties, and we couldn't.
So, assuming that we do not care about the not mapped topics,
we have created a~statement for more than 24\% of the facts.
If we restrict ourselves to the reviewed facts, a~set of 1.6M~facts
that have been human curated, we have far better results.
There are 0.58M~facts which subjects are mapped to Wikidata and 0.52M~of them
(\emph{i.e.}, 92\%) are converted into Wikidata statements.
And we would get another 1\% if we would be able
to map the properties \texttt{/people/person/weight\_kg}
and \texttt{/people/person/height\_meters} that Wikidata are not supporting yet.
58\% of the statements created from reviewed fact are already in Wikidata,
allowing us to add 0.25M~of new reviewed statements to Wikidata.

>>>>

In order to prepare the data for the integration into the Primary Sources Tool, we have created a set of scripts which map the content of the last Freebase dump into Wikidata statements.\footnote{The source code is available under the terms of the Apache~2.0 license here: \url{https://github.com/google/freebase-wikidata-converter}}.

Primary Sources has been developed at the same time as the mapping tool: we have first created a small dataset of around 1M statements based on a few properties (\texttt{/people/person/birth\_place}...) and deployed both the first dataset and a basic version of the tool in order to get user feedbacks. Then, we progressively had more statement to the tool database and made the opt-in process to use the tool inside of Wikidata easier, from a line to copy and paste in a user page to an option in user preference. So, we were able to both increase slowly the number of users of the tool and the size of the tool database.

The process of adding data by small batches of 1 or 2M each time allowed us to detect some performances issues in the tool and to fix them before they became too important. And other good effect is it allowed us to have quick feedbacks from the community about the already mapped data and, so, to adapt easily the mapping scripts and to fix quickly the data already in the tool.

\todo{Thomas: Proofread and expand}

@@

\todo{Sebastian or Thomas: write me}

@@

From the Freebase dump we have been able to create more than 17M~Wikidata claims
(\emph{i.e.}, statement without references) including 1.5M~IDs.
For that we have used 31M~facts.
When we add some references we get 19.6M~statements, and, after removing 1M~of duplicates
and the ones already in Wikidata, we obtain 14M~new statements.
So, if all these statements were added to Wikidata,
it would lead to a~21\% increase of Wikidata statements number.
But why are these numbers so low compared to the size of Freebase?
We believe that the main reason is that we have only mapped to Wikidata 4.56M~items, (\emph{i.e.},
only 9.5\% of Freebase topics), that are the subject of only 64M~facts.
So, we could not hope to map more than 64M~statements
assuming that we could map all reverse properties, and we couldn't.
So, assuming that we do not care about the not mapped topics,
we have created a~statement for more than 24\% of the facts.
If we restrict ourselves to the reviewed facts, a~set of 1.6M~facts
that have been human curated, we have far better results.
There are 0.58M~facts which subjects are mapped to Wikidata and 0.52M~of them
(\emph{i.e.}, 92\%) are converted into Wikidata statements.
58\% of the statements created from reviewed fact are already in Wikidata,
allowing us to add 0.25M~of new reviewed statements to Wikidata.
